\begin{thebibliography}{00}
	\bibitem{intro:thermo-analysis-federal}
	\emph{Анализ потребления тепловой энергии на отопление многоквартирных домов как способ повышения энергоэффективности в сфере ЖКХ} [Электронный ресурс] / Дирекция по проблемам ЖКХ //
	Аналитический центр при Правительстве Российской Федерации. --- 2013. --- Режим доступа:
	\url{http://gkh-altay.ru/d/205499/d/06_24_kr_stol_analitika_dor_abotannaya_po_rezultata_m.pdf} (дата обращения: 29.03.2017).

	\bibitem{intro:heating-drivers}
	\emph{Heating and cooling energy trends and drivers in buildings} / Ürge-Vorsatz D., Cabeza L. F., Serrano S., Barreneche C., Petrichenko K. //
	Renewable and Sustainable Energy Reviews --- Budapest, Hungary: Elsevier, 2015. --- \No{} 41 --- С. 85-98.

	\bibitem{intro:heat-loss-sources}
	\emph{What are the sources of home heat loss?} [Электронный ресурс] / Wilson L. //
	Shrink That Footprint --- Режим доступа: \url{http://shrinkthatfootprint.com/home-heat-loss} (дата обращения: 29.03.2017).

	\bibitem{intro:sources-residental}
	\emph{Detecting sources of heat loss in residential buildings from infrared imaging} [Электронный ресурс] / Chen S., Chen E. //
	Massachusetts Institute of Technology. Dept. of Mechanical Engineering --- 2011. --- Режим доступа: \url{http://hdl.handle.net/1721.1/68921} (дата обращения: 20.02.2017).

	\bibitem{intro:energy-use-perspective}
	\emph{Energy use in buildings in a long-term perspective} / Ürge-Vorsatz D., Petrichenko K., Staniec M., Eom J. //
	Current Opinion in Environmental Sustainability --- Budapest, Hungary: Elsevier, 2013. --- \No{} 5 --- С. 141-151.

	\bibitem{modeling:heat-technology}
	\emph{Geospatial Technologies to Improve Urban Energy Efficiency} / Hay G. J., Kyle C., Hemachandran B. et al. // Remote Sensing, 2011. --- \No{} 3(7) --- С. 1380-1405.

	\bibitem{problem:heat}
	\emph{HEAT: A web based system for residental waste heat analysis using airborne thermal imagery} [Электронный ресурс] / Hemachandran B., Hay G. J., Kyle C. D. // Department of Geography, University of Calgary --- 2010. --- Режим доступа: \url{http://www.isprs.org/proceedings/XXXVIII/part1/01/01_04_Paper_178.pdf} (дата обращения: 05.05.2017).

	\bibitem{problem:detection-windows-doors}
	\emph{Detection of windows and doors from thermal images by grouping geometrical features} / Sirmacek B., Hoegner L., Stilla U. //
	2011 Joint Urban Remote Sensing Event --- Germany, 2011.

	\bibitem{problem:aerial-oblique}
	\emph{Aerial oblique thermographic imagery for the generation of building 3D models to complement Geographic Information Systems} /  Lagüela S., Díaz-Vilariño L., Roca D., Armesto J. //
	QIRT Journal --- Germany, 2014.

	\bibitem{problem:thermal-leakages-facades}
	\emph{Thermal leakage detection on building facades using infrared textures generated by mobile mapping} / Hoegner L., Stilla U. //
	2009 Joint Urban Remote Sensing Event --- Germany, 2009.

	\bibitem{problem:knowledge-based-system}
	\emph{A knowledge-based system for the non-destructive diagnostics of façade isolation using the information fusion of visual and IR images} [Электронный ресурс] / Ribarić S., Marčetića D., Vedrinab D. S. // Faculty of Electrical Engineering and Computing, University of Zagreb --- 2008. --- Режим доступа: \url{http://www.sciencedirect.com/science/article/pii/S0957417408001425}, (дата обращения: 25.01.2017).

	\bibitem{problem:citizens-as-sensors}
	\emph{Citizens as sensors: the world of volunteered geography} / Goodchild, M. // GeoJournal, 2007. --- \No{} 69 --- C. 211–221.

	\bibitem{problem:vgi}
	\emph{VGI} [Электронный ресурс] : Материал из Википедии — свободной энциклопедии : Версия 755082720, сохранённая в 13:42 UTC 1 июня 2017 / Авторы Википедии // Википедия, свободная энциклопедия. — Электрон. дан. — Сан-Франциско: Фонд Викимедиа, 2017. — Режим доступа: \url{http://en.wikipedia.org/?oldid=755082720} (дата обращения: 02.06.2017).

	\bibitem{problem:myheat-utilities}
	\emph{MyHEAT - Utitlties} [Электронный ресурс] / MyHEAT, Inc. --- 2017 --- Режим доступа: \url{https://myheat.ca/utilities} (дата обращения: 02.05.2017).

	\bibitem{problem:nhm}
	\emph{National Heat Map} [Электронный ресурс] / Center for Sustainable Energy --- 2017 ---  Режим доступа: \url{https://www.cse.org.uk/projects/view/1183} (дата обращения: 02.05.2017).

	\bibitem{design:mvc}
	\emph{Model-View-Controller} [Электронный ресурс] : Материал из Википедии — свободной энциклопедии : Версия 85783223, сохранённая в 11:13 UTC 4 июня 2017 / Авторы Википедии // Википедия, свободная энциклопедия. — Электрон. дан. — Сан-Франциско: Фонд Викимедиа, 2017. — Режим доступа: \url{http://ru.wikipedia.org/?oldid=85783223} (дата обращения: 05.06.2017).

	\bibitem{design:rest}
	\emph{Architectural Styles and the Design of Network-based Software Architectures} / Fielding R. T. // The University of California, 2000.

	\bibitem{design:rest-uml}
	\emph{Overview of REST API Generation} [Электронный ресурс] / Visual Paradigm. Режим доступа: \url{https://www.visual-paradigm.com/support/documents/vpuserguide/276/3420/85153_overviewofre.html} (дата обращения: 05.06.2017).

	\bibitem{design:json}
	\emph{JSON} [Электронный ресурс] // Режим доступа: \url{http://json.org/} (дата
обращения: 27.03.2017).


\end{thebibliography}